\documentclass{resume}

\usepackage{marvosym}
\usepackage{makecell}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage[usenames,dvipsnames]{color}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


\begin{document}

\begin{center}
    \textbf{\Huge Tananov Artem } \\
    \small{
        \clink{
            \faEnvelope~\href{mailto:tananoff@icloud.com}{tananoff@icloud.com}  $\vert$
            {\faPhoneSquare~\fontdimen2\font=0.75ex +7 (981) 864-29-79} 
            $\vert$
            \faGithub~\href{https://github.com/AlwaraZs}{AlwaraZs}
        } \\
    }
\end{center}
    
     summary
     
     
\section{EDUCATION}{\small
    \begin{itemize}
        \item \textbf{ITMO University}\\
            {\footnotesize Studying for the bachelor degree in Computer Science and Applied Math}\\
            {\footnotesize 2019 - Present}
    \end{itemize}
}
    
\section{PROJECTS}{\small
    \begin{itemize}
        \item \clink{\href{https://github.com/AlwaraZs/parser}{\textbf{Parser} \color{black}~\faGithub}}\\
            {A calculator that can calculate the values ​​of expressions with three variables. The expression is parsed using the recursive descent method. Used Generics, Collections, OOP.}
        
        \item \clink{\href{https://github.com/AlwaraZs/dictionary/tree/main}{\textbf{Dictionary} 
        \color{black}~\faGithub}}\\
            {Spell check. Implementation of a utility for checking the spelling of Russian and English words. Used I/O, Collection FrameWork.}
            
        \item \clink{\href{https://github.com/AlwaraZs/mandelbrot}{\textbf{Mondelbrot} \color{black}~\faGithub}}\\
            {Implementation of the modndelbrot set with scalability. Used Qt, Multithreading.}
            
        \item \clink{\href{https://github.com/AlwaraZs/chess}{\textbf{Chess}  \color{black}~\faGithub }}\\
            {Classical chess was written without the implementation of queening a pawn. Used OOP.}
        
        \item \clink{\href{https://github.com/AlwaraZs/AAAgame}{\textbf{Role Playing Game} \color{black}~\faGithub}}\\
            {Typical simple AAA game. Used OOP, Multithreading.}
        
    \end{itemize}
}

\section{SKILLS}{\small
    \begin{itemize}
        \item \textbf {Java, C++}
        \item \textbf {PostgreSQL}
        \item \textbf {Git use basic commands to work with VCS}
        \item \textbf {I use MacOs as the main OS, I work with the terminal (I wrote bash scripts)}
    \end{itemize}
}

\section{LANGUAGES}{\small
    \begin{itemize}
        \item \textbf{Russian} 
            {\footnotesize Native}{}{}
        \item \textbf{English}
            {\footnotesize Intermediate}{}{}
    \end{itemize}
}
    
\section{miscellaneous}{\small
    \begin{itemize}
         {Now I am additionally taking the SkillFactory (Java developer) course. In elementary schools of varying degrees of complexity, all the missing skills are acquired in high quality, they want to work in cool / experienced programmers and I will apply the highest achievements to learn from them, develop programming skills, work in elementary schools and gain experience to become valuable in the future employee.} 
    \end{itemize}
}
\end{document}
